Hypertension and microbiome

### 2019-09-02 articletwo.Rmd
Minor

```{r bptreat numbers}
pseq.species %>% meta %>% pull(BP_TERAT) %>% summary
```

Hypertension prevalence

```{r test htn prevalence}
dset.alpha %>%
    dplyr::filter(BL_AGE < 60 + 12, BL_AGE > 60 - 12) %>%
    summarize(htn = sum(ifelse(HYPERTENSION == 1, 1, 0)), n = n(), proportion = htn/n) %>%
    kable
```

Minimum coefficient for alpha diversity is `r rbind(diversities$min,
diversities$max) %>% pull(estimate) %>% min`.

@@

```{r top pcoa genera}
df.genus.abund <- abundances(pseq.genus, transform = "compositional") %>%
    as.data.frame %>%
    tibble::rownames_to_column() %>%
    dplyr::mutate(rowname = make.names(rowname)) %>%
    gather(id, value, -rowname) %>% 
    spread(rowname, value)

>>>>

```{r bptreat numbers}
pseq.species %>% meta %>% pull(BP_TREAT) %>% summary
```

@@

```{r top pcoa genera, eval = FALSE}
df.genus.abund <- abundances(pseq.genus, transform = "compositional") %>%
    as.data.frame %>%
    tibble::rownames_to_column() %>%
    dplyr::mutate(rowname = make.names(rowname)) %>%
    gather(id, value, -rowname) %>% 
    spread(rowname, value)
